\documentclass[11pt]{letter}
% \linespread{1}
% \topmargin	= 0in	% Additional space added at the top margin
% \evensidemargin	= 1in    	% Additional space added at the left margin in odd pages
% \oddsidemargin	= 0in		% Additional space added at the left margin in even pages
% \textwidth	= 6.5in		% Width of the body of the page
% \textheight	= 9.0in		% Heigth of the body of the page
% \headsep	= 0.25in        % Distance between the header box and the body of the page 
% \headheight	= 0in		% Heigth of the box contained any header information
% \hoffset	= 0in 		%  1 inch horizontal offset
%\documentclass{letter}
\topmargin=-1in    % Make letterhead start about 1 inch from top of page 
\textheight=9.5in  % text height can be bigger for a longer letter
\oddsidemargin=0pt % leftmargin is 1 inch
\textwidth=6.5in   % textwidth of 6.5in leaves 1 inch for right margin
\textheight= 9in

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}
\signature{Henry R. Moncada}           % name for signature 
\longindentation=0pt                       % needed to get closing flush left
\let\raggedleft\raggedright                % needed to get date flush left
\begin{letter}{Dear Sir or Madame :}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \begin{flushleft}
% {\large\bf Henry R. Moncada}
% \end{flushleft}
% \medskip\hrule height .3pt
    \begin{minipage}{.35\linewidth}
    \begin{flushleft}
{\large\bf Henry R. Moncada}
    \end{flushleft}
  \end{minipage}
  \hfill
  \begin{minipage}{.55\linewidth}
    \begin{flushright}
{\large\bf hrmoncada@gmail.com/hrmoncada@lanl.gov}
    \end{flushright} 
  \end{minipage}
\medskip\hrule height .3pt
\begin{flushright}
\hfill 1469 Zepol Rd, Apt 110\\
\hfill Santa Fe, NM 87507, US\\
%\hfill hrmoncadalopez@miners.utep.edu\\
%\hfill hrmoncada@gmail.com/hrmoncada@lanl.gov\\
\hfill 915-730-2550
\end{flushright} 

\opening{}
I am writing to apply for OpenEye Scientific

%the Postdoctoral Computational Structural Biology and Computational Crystallography.
%Research Position in Computational Oncology
%Scientist - Statistical Geneticist at Helix, job position advertised.

The opportunity presented at research group is very appealing to me, and I believe that my strong technical experience and education will make me a very competitive candidate for this position.
The key strengths that I possess for success in this position include:
\begin{itemize}
 
 \item Passion for designed, developed and building new products and flexible to learn new areas of research as needed.
 \item Advanced knowledge in mathematical modeling and computational methods for simulations. Besides other projects, I want to point out that I did mathematical modeling of Chagas disease, and development python bioinformatics tools to predict genomic structures and analyze molecular sequences for the G protein-coupled receptors (GPCRs). In addition, I performance evaluation using BLAST and HTCondor job scheduler for workload management and multiple submission jobs.  You can find a brief description in my research statement.
 \item Teaching and mentoring and training people on complex technicals.
 \item Fluent in high-level programming languages (Python, Matlab, Fortran, C, and C++).
 \item Experience in code development and parallel computing.
 \item Strong background in numerical analysis, numerical linear algebra, and numerical ODE and PDE.
 \item Proficient using Linux/Unix environment 
 \item Image processing and implementing simulation in 3D.
 \item Experience analysing and modeling small angle X-ray diffraction superlattices devices data .
\end{itemize}
My background includes a Ph.D. degree in Computational Science, MS in Applied Mathematics and BS in Physics, 
I have a full understanding of the lifecycle of a software development project. I also have experience in learning and excelling at new technologies as needed.
Please see my resume for additional information on my experience. Thank you for your time and consideration. I look forward to speaking with you about this employment opportunity.

I can be reached anytime via email at \verb+hrmoncada@gmail.com+, or my cell phone, \verb+915-730-2550+.

\closing{Sincerely yours,} 
\end{letter}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\end{document}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
